D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-17 ootavacuous.tex
Alan Stern February 16 feedback
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem}

@@

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as too restrictive, in that a given piece
of code should either contain or not contain a semantic dependency
independent of the implementation used to run it.

@@

void thread2() {
   int r2 = y;
   x = r2;
}
\end{verbatim}
\end{quote}
A compiler using global analysis and treating \co{x} and \co{y} as
quasi-volatile objects could omit the two loads, replacing them in the
machine code with simple assignments ``\co{r1 = 42}'' and
``\co{r2 = 42}''.
This would be a valid transformation, and the resulting behavior would
not count as OOTA because according to our definition, the
dependencies in \co{thread1} and \co{thread2} would not be semantic.

>>>>

\begin{document}
\title{D3064R0: How to Avoid OOTA Without Really Trying}

@@

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as avoiding the real problem, in that a given
piece of code should either contain or not contain a semantic dependency
independent of the implementation used to run it.

@@

void thread2() {
   int r2 = y;
   x = r2;
}
\end{verbatim}
\end{quote}
A compiler using global analysis and treating \co{x} and \co{y} as
quasi-volatile objects could omit the two loads, replacing them in the
machine code with simple assignments ``\co{r1 = 42}'' and
``\co{r2 = 42}''.
This would be a valid transformation, and the resulting behavior would
not count as OOTA according to our definition because the
dependencies in \co{thread1} and \co{thread2} would not be semantic.
